name: concepts
class: center, middle, inverse

# Git concepts

---

## The main components of a Git repository

```{r repo-comp}
knitr::include_graphics("figs/repo-comp.svg")
```

---

## Add: stage changes for committing

```{r git-add}
knitr::include_graphics("figs/git-add.svg")
```

---

## Commit: append staged changes to history

```{r git-commit}
knitr::include_graphics("figs/git-commit.svg")
```

---

## Push: changes on local repo ⭢ remote repo

```{r git-push}
knitr::include_graphics("figs/git-push.svg")
```

---

## Push: changes on local repo ⭢ remote repo (before)

```{r git-push-before}
knitr::include_graphics("figs/git-push-before.svg")
```

---

## Push: changes on local repo ⭢ remote repo (after)

```{r git-push-after}
knitr::include_graphics("figs/git-push-after.svg")
```


---

## Pull: changes on remote repo ⭢ local repo (before)

```{r git-pull-before}
knitr::include_graphics("figs/git-pull-before.svg")
```

---

## Pull: changes on remote repo ⭢ local repo (after)

```{r git-pull-after}
knitr::include_graphics("figs/git-pull-after.svg")
```
